|

### 2024-08-07 doc/paper.qmd
update paper

---
title: |
  | Earnings Management and Investor Protection:
  | Accounting Reading Group - Assignment III\vspace{1cm}
author:
  - name: Melisa Mazaeva
    email: melisa.mazaeva@student.hu-berlin.de
    affiliations:
      - Humboldt-Universität zu Berlin  
date: today
date-format: MMM D, YYYY [\vspace{1cm}]
abstract: |
  | This project uses the TRR 266 Template for Reproducible Empirical Accounting Research (TREAT) to provide an infrastructure for open science-oriented empirical projects. Leveraging external Worldscope data sets on financial data, the repository showcases a reproducible workflow that integrates Python scripts for data analysis. The project’s output demonstrates a comprehensive application of skills to replicate and extend the findings from the seminal paper by Leuz, Nanda, and Wysocki (2003), particularly in providing descriptive statistics for the four individual earnings management measures as well as the aggregate earnings management score across various countries. In doing so, it documents and discusses the research design choices made and the variations between the original and reproduced results. This code base, adapted from TREAT, should give you an overview on how the template is supposed to be used for my specific project and how to structure a reproducible empirical project.
  | \vspace{6cm}
bibliography: references.bib
biblio-style: apsr
format:
  pdf:
    documentclass: article
    number-sections: true
    toc: false
fig_caption: yes
fontsize: 11pt
ident: yes
always_allow_html: yes
header-includes:
  - \usepackage[nolists]{endfloat}    
  - \usepackage{setspace}\doublespacing
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{0em}
  - \usepackage[hang,flushmargin]{footmisc}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=24pt,font=bf}
  - \usepackage{array}
  - \usepackage{threeparttable}
  - \usepackage{adjustbox}
  - \usepackage{graphicx}
  - \usepackage{csquotes}
  - \usepackage{indentfirst}  # Added this line to ensure the first paragraph is indented for better readability
  - \usepackage[margin=1in]{geometry}
---

@@

# Introduction

@@

# Research Design Choices and Assumptions

@@

By following the steps provided in Section 4 and adhering to the assumptions made, I successfully replicated the analysis and produced the required table. A thorough step-by-step approach, with each step clearly documented, helped to understand and verify the outputs.

# Replication Steps
## Step 1: Pulling the Data and Managing the Databases
In contrast to Assignment I, where the data was provided externally, Assignment III involves additionally pulling data directly from the Worldscope database, merging relevant tables, and preparing the data for further analysis from raw data to final output.

@@

During the preparation step, 8,265 firms and 20,521 firm-year observations (all due to second filtration step) were dropped, resulting in a final dataset with 18,040 firms and 123,469 firm-year observations. The differences in the numbers between the prepared dataset and the figures mentioned in the paper (70,955 firm-year observations and 8,616 non-financial firms) could be due to the assumptions listed in Section 3.

>>>>

---
title: |
  | Earnings Management and Investor Protection:
  | Accounting Reading Group - Assignment III\vspace{1cm}
author:
  - name: Melisa Mazaeva
    email: melisa.mazaeva@student.hu-berlin.de
    affiliations:
      - Humboldt-Universität zu Berlin  
date: today
date-format: MMM D, YYYY [\vspace{1cm}]
abstract: |
  | This project uses the TRR 266 Template for Reproducible Empirical Accounting Research (TREAT) to provide an infrastructure for open science-oriented empirical projects. Leveraging external Worldscope data sets on financial data, the repository showcases a reproducible workflow that integrates Python scripts for data analysis. The project’s output demonstrates a comprehensive application of skills to replicate and extend the findings from the seminal paper by Leuz, Nanda, and Wysocki (2003), particularly in providing descriptive statistics for the four individual earnings management measures as well as the aggregate earnings management score across various countries. In doing so, it documents and discusses the research design choices made and the variations between the original and reproduced results. This code base, adapted from TREAT, should give you an overview on how the template is supposed to be used for my specific project and how to structure a reproducible empirical project.
  | \vspace{6cm}
bibliography: references.bib
biblio-style: apsr
format:
  pdf:
    documentclass: article
    number-sections: true
    toc: false
fig_caption: yes
fontsize: 11pt
ident: yes
always_allow_html: yes
number-sections: true 
header-includes:
  - \usepackage[nolists]{endfloat}    
  - \usepackage{setspace}\doublespacing
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{0em}
  - \usepackage[hang,flushmargin]{footmisc}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=24pt,font=bf}
  - \usepackage{array}
  - \usepackage{threeparttable}
  - \usepackage{adjustbox}
  - \usepackage{graphicx}
  - \usepackage{csquotes}
  - \usepackage{indentfirst}  # Added this line to ensure the first paragraph is indented for better readability
  - \usepackage[margin=1in]{geometry}
---

@@

# Introduction {#sec-introduction}

@@

# Research Design Choices and Assumptions {#sec-research_design_assumptions}

@@

By following the steps provided in @sec-replication_steps and adhering to the assumptions made, I successfully replicated the analysis and produced the required table. A thorough step-by-step approach, with each step clearly documented, helped to understand and verify the outputs.

# Replication Steps {#sec-replication_steps}
## Step 1: Pulling the Data and Managing the Databases
In contrast to Assignment I, where the data was provided externally, Assignment III involves additionally pulling data directly from the Worldscope database, merging relevant tables, and preparing the data for further analysis from raw data to final output.

@@

During the preparation step, 8,265 firms and 20,521 firm-year observations (all due to second filtration step) were dropped, resulting in a final dataset with 18,040 firms and 123,469 firm-year observations. The differences in the numbers between the prepared dataset and the figures mentioned in the paper (70,955 firm-year observations and 8,616 non-financial firms) could be due to the assumptions such as variations in initial datasets, data updates, and filtering criteria listed in @sec-research_design_assumptions. However, the original study might have included additional data cleaning steps not explicitly mentioned, such as handling outliers, specific industry exclusions, or other criteria, which could affect the final counts.
